A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-14 Paper.tex
Deleting graph and fast salm

		\subsection{Delayed/Offline initializations}
			These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman},a posed based ekf as mentioned in \cite{Webster}, a moving horizon estimation as mentioned in \cite{SenWang2013} etc. The most popular ones are mentioned below.

@@

	\subsubsection{Trilateration}
		\cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection. Rings are drawn at different points of the robots path as shown in Fig[a] , where the radius of the rings depend on the strength of the received signals from the beacons. This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c]. %more papers needed

@@

\begin{figure}[h!]
	\centering
	\includegraphics[height=70mm,width=90mm]{graph_slam.PNG}
	\caption{$z_k,\mu_k,x_k$ represents the measurement contraints, velocity constraints and the the robot path.}

\subsection{Graph SLAM}
Graph SLAM unlike the EKF solves the full SLAM problem. It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix. The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in\cite{Thrun2002a}. This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.

It represents the information in the form of a graph as show in figure. The nodes in the graph represent the robots path and the landmarks. The edges between them represents the spatial  constraints between them also known as information constraints. These constraints ae then linearized and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.

\subsection{Particle}      %change the references
Particles filters are made ue up various monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks. It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainty through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

@@

	\subsection{Fast SLAM}
	EKF is mainly used when we have a non-linear dynamic system model which has Gaussian noise.The quadratic complexity due to Gaussian approximations of higher dimensions make the covariance matrix very large. This eventually causes higher complexity and leads to the divergence of the filter. The single data association problem also adds to this complexity. FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem. This allows it handle system models with non Gaussians noise as well. This results in the computational complexity to grow logarithmically instead of quadratic growth.

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence, in FastSLAM the robot path is initialized by using a particle filter. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}. Thus, it maintains multiple data hypothesis overcoming the EKF problem.

	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficiency. In order to overcome this the algorithm was tweaked to have a better target distribution in FASTSLAM 2.0. It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}

>>>>

		\subsection{Delayed/Offline initializations}
			These are methods that perform delayed localizations  where initially the robot moves around offline collects some measurements and then initializes the location of the landmarks. This can be undersirable as it causes a delay in the localization of the robot whenever there is a immediate real time application such as in autonomous vehicles. Localization can be performed only once a accurate estimations of the beacons are made. There are several offline algorithms that perform localization such as the least squares approach in \cite{Newman}, a posed based ekf as mentioned in \cite{Webster2012}, a moving horizon estimation as mentioned in \cite{Vallicrosa2014a} etc. The most popular ones are mentioned below.

@@

	\subsubsection{Trilateration}
		\cite{Thrun2002} mentions a basic trilateration technique involving geometric intersection. Rings are drawn at different points of the robots path as shown in Fig[a], where the radius of the rings depend on the strength of the received signals from the beacons. This method of initialization is highly ambiguous as the rings can have more than 1 point of intersecting as shown in Fig[b]  or no  intersecting points as shown in Fig[c]. %more papers needed

@@

\subsection{Particle Filters}      %change the references
Particles filters are made ue up various monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks. It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainty through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

@@

In /cite{Blanco2008a} uses the particle filter to overcome the delayed initialization issue brought forward by RO SLAM. It uses the Rao-Blackwellized Particle filter to maintain a conditional distribution for each beacon which eventually is transformed into a EKF when the uncertainty becomes sufficiently small. This approach is validated for both simulated and real data sets. This approach is preferred in indoor applications where there is a high probability of multi path signal propagation.
